Seasonal Adaptation

### 2019-11-23 writing/manuscript.Rmd
parameter table added

>>>>

| Default Parameters               |      |
|----------------------------------|------|
| Crossover probability            | 0.05 |
| Mutation probability             | 10   |
| Population size                  | 500  |
| Number of loci                   | 100  |
| Exponent of the fitness function | 1    |
| Dominance                        | 0.5  |
| Years                            | 100  |
| Generations per year             | 20   |
| Seasonal balance                 | 2    |
